Remark on the hypothetical judgment

### 2015-10-16 paper.tex
Add section on inference vs consequence

>>>>

\subsection{What is the difference between an inference rule and a hypothetical judgment?}

Is a rule of inference really the same as a consequence or hypothetical
judgment, as Martin-L\"of claimed? One way to elucidate the differences
is to consider them in the context of a Beth or Kripke semantics.

The validity of an inference rule $\infer{\JJ_2}{\JJ_1}$ at a world lies in an
effective transformation of experiences of $\JJ_1$ at that world to experiences
of $\JJ_2$ at that world; on the other hand, to experience a hypothetical
judgment $\HypJ{\JJ_2}{\JJ_1}$ at a world is to have a means to transform
experiences of $\JJ_1$ at any future world into experiences of $\JJ_2$.

Construed in this way, judgments can be explained by specifying when/where they
are forced; it is a reasonable requirement that if we shall consider $\JJ$ to
be a judgment, then for any worlds $u\preceq v$, from $u\Vdash\JJ$ we may
conclude $v\Vdash\JJ$ (this is called \emph{monotonicity}). The hypothetical
judgment, at least as explained above, preserves the monotonicity of knowledge
by definition, whereas rules of inference may not in general satisfy this property.

On the contrary, an "admissible rule" $\infer{\JJ_2}{\JJ_1}$ is sensitive to
changes in the state of knowledge, and may cease to be valid if a previously
unknown way to experience $\JJ_1$ is found. Such rules may only be construed as
hypothetical judgments if the acts specified by the meanings of their premises
are sufficiently circumscribed so as to satisfy the monotonicity requirement.

Martin-L\"of's identification of the rules of logic with hypothetical judgments, then,
only obtains because the concepts of \emph{verification} of a proposition, and
(secondarily) \emph{truth} of a proposition are fixed in advance for all time
by means of \emph{canonical forms} and \emph{computation} respectively.
